%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MASTER RESUME – Gundeep Singh Bali
% Combined from 6 resume PDFs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,letterpaper]{article}

% ---- Packages ----
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{qrcode}

% ---- Page Geometry ----
\geometry{left=0.55in, right=0.55in, top=0.65in, bottom=0.6in}

% ---- Colors ----
\definecolor{accent}{HTML}{1a5276}

% ---- Formatting ----
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% ---- Section Formatting ----
\titleformat{\section}
  {\vspace{6pt}\scshape\raggedright\large\color{accent}}
  {}{0em}
  {}
  [\color{accent}\titlerule\vspace{-4pt}]

\titleformat{\subsection}
  {\vspace{1pt}}
  {}{0em}
  {}

% ---- Custom Commands ----
\newcommand{\subsecitem}[4]{
  {\textbf{#1}} \hfill {\small\textit{#2}}\\
  {\small\color{accent}#3} \hfill {\small\textit{#4}}\\
  \vspace{-2pt}
}

\newcommand{\bulletitem}[1]{
  \vspace{-2pt}
  \begin{itemize}[leftmargin=1.2em, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item \small{#1}
  \end{itemize}
  \vspace{-2pt}
}

\newcommand{\bigbullet}[1]{
  \begin{itemize}[leftmargin=1.2em, itemsep=-1pt, topsep=-2pt, parsep=0pt, partopsep=0pt]
    \item \small{#1}
  \end{itemize}
}

\begin{document}

% ---- Header ----
\begin{center}
  {\Huge\scshape\textbf{Gundeep Singh Bali}}\\[4pt]
  \small
  \faEnvelope\enspace\href{mailto:gundeep240800@gmail.com}{gundeep240800@gmail.com}
  \enspace\textbar\enspace
  \faLinkedinIn\enspace\href{https://linkedin.com/in/gundeep}{LinkedIn}
  \enspace\textbar\enspace
  \faGithub\enspace\href{https://github.com/gundeep}{GitHub}
  \enspace\textbar\enspace
  \faGlobe\enspace\href{https://gundeep.dev}{Personal Website}
  \enspace\textbar\enspace
  \faGamepad\enspace\href{https://gundeep.itch.io}{Itch.io}\\[2pt]
  \faMedium\enspace\href{https://medium.com/@gundeep}{Medium}
  \enspace\textbar\enspace
  \faTwitter\enspace\href{https://bsky.app/profile/gundeep}{Bluesky}
  \enspace\textbar\enspace
  \faYoutube\enspace\href{https://youtube.com/@gundeep}{YouTube Shorts}
\end{center}

% ---- Summary ----
\section{Summary}
\small{
Full Stack Mobile Developer and Software Engineer with expertise in React Native, Rust, Godot, and TypeScript.
Experienced in building high-performance systems — from microservices architectures and payment integrations
to low-latency async networking (5{,}000{\texttimes} speed improvement, 1\,s $\rightarrow$ 200\,µs).
Published game developer since 2020 with projects in Godot and Bevy (ECS). Active open source contributor
to projects with 30M+ users including Bluesky, FreeCodeCamp, Godot, Mattermost, LazyGit, and Memos.
Also experienced in social media strategy, content creation, and video editing for tech platforms.
}
\vspace{-4pt}

% ---- Professional Experience ----
\section{Professional Experience}

\subsecitem{Ravencast Labs}{Present, Remote}
          {Rust \& Web3 Developer \textbar{} Tokio, Actix, Python, TypeScript, Web3.js}
          {}
\bigbullet{Reduced system latency by \textbf{5{,}000{\texttimes}} — from 1 second to 200 microseconds (99.98\% faster) — by implementing a backup socket connection for seamless failover.}
\bigbullet{Designed and optimized high-performance async services using Tokio \& Actix, processing millions of real-time events with multi-threaded concurrency models.}
\bigbullet{Built fault-tolerant reconnection workflows with message checkpointing (clk, initialClk) and comprehensive unit/integration test harnesses.}
\bigbullet{Developed a Python quoter client with TCP sockets handling cache for orders and market streams from the Rust betting server.}
\bigbullet{Built Telegram AI Agent bots for Solana meme coins: trending news, holder analysis, liquidity analysis, wallet creation/import, and trade execution on Meteora.}
\bigbullet{Implemented quote fetching and transaction execution logic for DLMM, DBC, and DAMM liquidity pools using web3.js and TypeScript.}
\bigbullet{Analyzed wealth distribution of Solana accounts using \textbf{Gini and Theil inequality} metrics; assessed DEX liquidity distribution across Solana.}

\vspace{2pt}
\subsecitem{Ensemble Control / Rewardwise}{May 2024 -- Dec 2024, Remote}
          {Full Stack Mobile Developer \textbar{} React Native, Django, Docker, Linux}
          {}
\bigbullet{Developed and managed a \textbf{microservices architecture} with \textasciitilde8 services, ensuring scalability and maintainability.}
\bigbullet{Implemented \textbf{image compression} reducing file sizes by up to 90\%, significantly cutting bandwidth costs and server load.}
\bigbullet{Integrated \textbf{anti-root detection} mechanism and \textbf{image metadata/geo-location stripping} for enhanced privacy and security.}
\bigbullet{Led full-stack integration of \textbf{Tilled payment API} (U.S.) and \textbf{Eazebuzz payment API}, covering frontend UI and backend transaction processing.}
\bigbullet{Created a \textbf{Slack bot} (Python) for real-time Django server error notifications, enabling non-technical teams to access logs without SSH.}
\bigbullet{Patched a \textbf{session login vulnerability} that could allow unauthorized access; developed a custom graphing library using \texttt{react-native-svg} powering merchant heatmaps and analytics dashboards.}

\vspace{2pt}
\subsecitem{Codewick}{Dec 2023 -- Feb 2024, Remote}
          {Mobile Developer Intern \textbar{} React Native, Bluetooth, Git}
          {}
\bigbullet{Engineered a \textbf{Bluetooth communication system} for seamless thermal printer integration, enabling direct bill printing from the mobile app.}
\bigbullet{Developed \textbf{inventory management systems} for staff and stock tracking, improving operational efficiency.}

% ---- Game Development ----
\section{Game Development (Hobbyist/Volunteer)}

\subsecitem{Indie Game Developer}{2020 -- Present}
          {Godot, GDScript, Bevy (Rust), Aseprite, Shader Development}
          {}
\bigbullet{Built and published multiple \textbf{2D game prototypes} on Itch.io, including a Tomb of the Mask-inspired vertical scroller.}
\bigbullet{Created a \textbf{Stoneshard-like RPG} in just 2 days for a mini-game-jam, featuring inventory, combat, and procedural dungeon elements (\href{https://x1vi.itch.io/rpg-game-testing-can-break}{Link}).}
\bigbullet{Created custom visual effects: \textbf{water ripple shaders}, sky shaders, and other real-time effects using Godot Shader Language.}
\bigbullet{Built a modular \textbf{RPG inventory system} in Rust using Bevy and ECS architecture for flexibility and scalability.}
\bigbullet{Designed \textbf{pixel art assets} and UI elements with Aseprite, handling both visual design and programming.}

% ---- Open Source Contributions ----
\section{Open Source Contributions}

\bigbullet{\href{https://github.com/godotengine/godot}{\textbf{Godot}} (105k+ stars, C++/GDScript) --- Fixed a bug in the text edit core engine component affecting in-game UI that the community had to work around for years.}
\vspace{1pt}
\bigbullet{\href{https://github.com/Redot-Engine/redot-engine}{\textbf{Redot}} (5k+ stars, C++/GDScript) --- Applied the same text edit fix to the Redot fork, benefiting both engine communities.}
\vspace{1pt}
\bigbullet{\href{https://github.com/bluesky-social/social-app}{\textbf{Bluesky}} (30M+ users, React Native/TypeScript/Golang) --- Implemented QR code profile sharing; built a custom scroll bar for homepage usability; fixed a bug preventing unfollow of blocked accounts.}
\vspace{1pt}
\bigbullet{\href{https://github.com/usememos/memos}{\textbf{UseMemos}} (4.6M Docker Pulls, React/TypeScript/Golang) --- Fixed Mermaid diagram theme inconsistencies, memo collapsing issues, and a misconfiguration bug with Disallow Password Authentication switch.}
\vspace{1pt}
\bigbullet{\href{https://github.com/jesseduffield/lazygit}{\textbf{LazyGit}} (1M+ users, Golang) --- Added a feature to filter commit history by date range for efficient navigation.}
\vspace{1pt}
\bigbullet{\href{https://github.com/freeCodeCamp/freeCodeCamp}{\textbf{FreeCodeCamp}} (1M+ users, React/TypeScript/MongoDB) --- Introduced persistent pane state saving; enhanced debugging system allowing repeated test runs without auto-redirect.}
\vspace{1pt}
\bigbullet{\href{https://github.com/mattermost/mattermost}{\textbf{Mattermost}} (500K+ users, React/TypeScript) --- Enhanced emoji picker with persistent selection across sessions.}

% ---- Additional Projects ----
\section{Additional Projects}

\bigbullet{\textbf{Dioxus Arti Client} (Rust, Tokio, Axum, Serde) --- Set up a Dioxus mobile environment integrated with Tor browsing via Arti Client for anonymous browsing.}
\bigbullet{\textbf{CLI Stock Screener} (Rust, Grow API) --- Built a command-line momentum strategy screener for stock market analysis.}
\bigbullet{\textbf{Rust Betting Systems \& Bot Infrastructure} --- Developed high-performance betting systems integrated with multiple real-time data sources; built Telegram bots for automated trading and monitoring.}

% ---- Skills ----
\section{Skills}

\begin{flushleft}
\small
\textbf{Languages:} \hspace{2pt} Rust, TypeScript, Python, GDScript, C++, Go, Elixir, JavaScript \\
\vspace{1pt}
\textbf{Frameworks \& Runtimes:} \hspace{2pt} React Native, React, Django, Tokio, Actix, Axum, Serde, Bevy (ECS) \\
\vspace{1pt}
\textbf{Game Engines \& Tools:} \hspace{2pt} Godot, Bevy, Macroquad, Aseprite, Shader Development \\
\vspace{1pt}
\textbf{DevOps \& Tooling:} \hspace{2pt} Docker, Git, GitHub, Linux (Ubuntu), WSL, Figma, CI/CD \\
\vspace{1pt}
\textbf{Security:} \hspace{2pt} Metasploit, Burp Suite, OWASP ZAP, MOBSf, Anti-root Detection \\
\vspace{1pt}
\textbf{Social Media \& Content:} \hspace{2pt} Instagram, Twitter/Bluesky, YouTube, LinkedIn, Canva, CapCut, KdenLive, Shotcut, Adobe Express, Google Analytics \\
\vspace{1pt}
\textbf{Domains:} \hspace{2pt} Web3/Blockchain (Solana, Meteora, Betfair), Low-Latency Systems, Game Development, Mobile Development, Digital Marketing
\end{flushleft}

% ---- Education ----
\section{Education}

\subsecitem{Chandigarh Group of Colleges, Punjab}{2019 -- 2023}
          {Bachelor of Technology (B.Tech) in Computer Science and Engineering}
          {}

% ============================================
% QR Code Reference Sheet
% ============================================
\newpage
\begin{center}
  {\Large\scshape\textbf{Quick Links — QR Codes}}\\[10pt]
  \small Scan any code to visit the corresponding link.\\[12pt]
  \begin{tabular}{c c c}
    % Row 1
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{mailto:gundeep240800@gmail.com}\\[4pt]
      {\small Email}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://linkedin.com/in/gundeep}\\[4pt]
      {\small LinkedIn}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/gundeep}\\[4pt]
      {\small GitHub}
    \end{minipage}
    \\[14pt]
    % Row 2
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://gundeep.dev}\\[4pt]
      {\small Personal Website}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://gundeep.itch.io}\\[4pt]
      {\small Itch.io Portfolio}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://x1vi.itch.io/rpg-game-testing-can-break}\\[4pt]
      {\small RPG Game (Itch.io)}
    \end{minipage}
    \\[14pt]
    % Row 3
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://medium.com/@gundeep}\\[4pt]
      {\small Medium Blog}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://bsky.app/profile/gundeep}\\[4pt]
      {\small Bluesky}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://youtube.com/@gundeep}\\[4pt]
      {\small YouTube Shorts}
    \end{minipage}
    \\[14pt]
    % Row 4
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/godotengine/godot}\\[4pt]
      {\small Godot Engine (PR)}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/Redot-Engine/redot-engine}\\[4pt]
      {\small Redot Engine (PR)}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/bluesky-social/social-app}\\[4pt]
      {\small Bluesky (OSS)}
    \end{minipage}
    \\[14pt]
    % Row 5
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/usememos/memos}\\[4pt]
      {\small UseMemos (PRs)}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/jesseduffield/lazygit}\\[4pt]
      {\small LazyGit (PR)}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/freeCodeCamp/freeCodeCamp}\\[4pt]
      {\small FreeCodeCamp (PRs)}
    \end{minipage}
    \\[14pt]
    % Row 6
    \begin{minipage}{0.3\textwidth}
      \centering
      \qrcode[height=1.4in,level=H]{https://github.com/mattermost/mattermost}\\[4pt]
      {\small Mattermost (PR)}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \phantom{\qrcode[height=1.4in,level=H]{https://github.com/mattermost/mattermost}}
    \end{minipage}
    &
    \begin{minipage}{0.3\textwidth}
      \centering
      \phantom{\qrcode[height=1.4in,level=H]{https://github.com/mattermost/mattermost}}
    \end{minipage}
  \end{tabular}
\end{center}

\end{document}
